Cancer Applications of Choropleth Maps, and the Potential of Cartograms and Alternative Map Displays

### 2019-12-18 review_article.Rmd
election mapping references

---
title: "Cancer Applications of Choropleth Maps, and the Potential of Cartograms and Alternative Map Displays"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: no
    toc_depth: 3
    dev: jpeg
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage{fancyhdr}\pagestyle{fancy}\fancyhead[R]{\thepage}
link-citations: yes
fontsize: 11pt
geometry: margin = 1.2in
csl: springer-vancouver.csl
yolo: yes
---

@@

## Tile Map
<!-- 173 words -->
A tile map provides a tessellated display of consistent shapes.  A similar method to a rectangular cartogram, represents each geographic area using a square. The squares are tessellated to create a grid. Each area is represented by a square of the same dimensions, each tile is usually one unit of measurement, this could be geographic regions such as states or population-based that use a consistent measure of population for each tile. Regions with over four neighbors require some necessary displacement. The tile map uses color to represent a value of a statistic for each area. A similar method to a rectangular cartogram represents each geographic area using a square of the same dimensions. There are online media sources using this method, these include [NPR](https://www.npr.org/2016/10/18/498406765/npr-battleground-map-hillary-clinton-is-winning-and-its-not-close), [FiveThirtyEight](https://projects.fivethirtyeight.com/2016-election-forecast/), [The Wall Street Journal](http://graphics.wsj.com/elections/2016/2016-electoral-college-map-predictions/), [The Washington Post](https://www.washingtonpost.com/graphics/politics/2016-election/50-state-poll/). Tile maps may be difficult to create as they are best created manually, they require additional time and care as the number of geographic areas to include increases.
<!-- cite mosaic cartograms -->

>>>>

---
title: "Cancer Applications of Choropleth Maps, and the Potential of Cartograms and Alternative Map Displays"
author: "Stephanie Kobakian^[Science and Engineering Faculty, Queensland University of Technology.], Dianne Cook^[Faculty of Econometrics and Business Statistics, Monash University.] and Jessie Roberts^[Queensland University of Technology.]"
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: no
    toc_depth: 3
    dev: jpeg
header-includes:
    - \usepackage{setspace}\doublespacing
link-citations: yes
bibliography: reviewbib.bib
fontsize: 11pt
geometry: margin = 1.2in
csl: springer-vancouver.csl
yolo: yes
---

@@

## Tile Map
<!-- 173 words -->
A tile map provides a tessellated display of consistent shapes.  A similar method to a rectangular cartogram, represents each geographic area using a square. The squares are tessellated to create a grid. Each area is represented by a square of the same dimensions, each tile is usually one unit of measurement, this could be geographic regions such as states or population-based that use a consistent measure of population for each tile. Regions with over four neighbors require some necessary displacement. The tile map uses color to represent a value of a statistic for each area. A similar method to a rectangular cartogram represents each geographic area using a square of the same dimensions. There are online media sources using this method, these include [@NPR], [@FiveThirtyEight], [@WSJ], [@WP]. Tile maps may be difficult to create as they are best created manually, they require additional time and care as the number of geographic areas to include increases.
<!-- cite mosaic cartograms -->
